Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-30 writing/nips_submission/response/EML_response.tex
slowly getting better

\begin{document}
\begin{wrapfigure}{r}{0.27\textwidth}
\begin{center}
\begin{tikzpicture}[auto, scale=0.75]
\node at (-1.5, -3.5) (examples) {Examples};
\node at (-1.5, -2.5) (D1) {
\(\left\{
\begin{matrix}
(z^{ex}_{in,0}, z^{ex}_{targ,0})\\
$\vdots$
\end{matrix}\right\}\)};

@@

\vspace{-1.5em}

@@

\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. We would like to clarify how the architecture functions and how it is novel. To begin, we will clarify how a basic polynomial like $x + 1$ is learned. This is depicted schematically in the figure. As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e. the polynomial value) at each point. The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding. Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, then max pools elementwise across them, and then applies two more layers of processing to produce the function embedding which represents this polynomial. This procedure is permutation invariant by design. We then pass the function embedding $z^{func}$ through the hyper network $\mathcal{H}$ to parameterize a function $F$ which ideally performs the mapping from inputs to outputs. We can then take a new set of probe inputs (i.e. points we want to evaluate the polynomial at), transform them according to $F$ to produce a set of predictions, and then train the model or evaluate it if we have targets. As the reviewers noted, this is similar to many existing meta-learning approaches. \par 

@@

\textbf{The insight of our paper is that meta-mappings over polynomials are exactly analogous to basic meta-learning of a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for a more abstract function that operates over polynomials (e.g. multiplying by 2). These polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding. We then can take these pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for this meta-task. Just as above, we can pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are 1) where the inputs and targets come from and 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task. To evaluate the real performance on a meta-mapping, we actually computed the performance of the predicted output embedding at regressing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding inputs to this function, and then measuring its predicted outputs. We hope this clarifies how our architecture works, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, but the architectural contribution of our paper is to show a way that meta-mappings can be parsimoniously integrated into a meta-learning architecture without adding a single parameter. We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings. These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points, so we are revising the main text to clarify this. \par 

@@

\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary. We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, and we see alternatives as an exciting future direction. Our work proposes the challenge of meta-mappings, and a starting point for thinking about the solutions. A note on the DQN: the problem as we have defined it is not exactly a standard supervised problem because you only observe the reward for the action you execute, but we are not using a full DQN. \par 

@@

\textbf{miniImageNet:} TBD. \par

@@

\textbf{Datasets:} The polynomials and cards tasks are implemented as stand-alone python modules that other researchers can use, and will be released on github. Creating complex datasets for meta-mappings is an important future direction. \par

@@

\textbf{Natural language:} Language was simply used as a meta-mapping cue in the main text (but c.f. appendix A). Specifically, we used the language embedding as input to the hyper network to generate the meta-mapping parameters. \par
\textbf{Continual learning:} Any architecture which generates task embeddings could cache them, but we have not seen prior work suggest this. This approach does requires storing an embedding vector per task, but many other approaches (such as EWC) require storing an extra ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional embedding per task would consume less memory than doubling the parameter count, even up to millions of tasks. We think this observation is somewhat interesting, but it is not the main point of our article, so we have slightly de-emphasized it in the main text. \par

>>>>

\begin{document}
\begin{wrapfigure}{r}{0.27\textwidth}
\begin{center}
\vspace{-0.85em}
\begin{tikzpicture}[auto, scale=0.75]
\node at (-1.5, -3.5) (examples) {Examples};
\node at (-1.5, -2.5) (D1) {
\(\left\{
\begin{matrix}
(z^{ex}_{in,0}, z^{ex}_{targ,0})\\
$\vdots$
\end{matrix}\right\}\)};

@@

\vspace{-2.3em}

@@

\textbf{Architecture \& contributions:} We agree with the reviewers that the most novel contribution of our paper is the proposal to think about transfer in terms of meta-mappings and task transformations. We would like to clarify the architecture and training. First we will clarify how a basic polynomial is learned. This is depicted schematically on the right. As in standard meta-learning, we generate a set of examples, consisting of tuples of input point, and the target output (i.e. the polynomial evaluated at that point). The meta-network $\mathcal{M}$ processes this set of (embedded input, embedded target) pairs to produce a function embedding. Specifically, it concatenates each pair, applies two layers of identical processing to each concatenated pair independently, max pools elementwise across them, and then applies two more layers of processing to produce the function embedding $z^{func}$ for this polynomial. We pass the function embedding through the hyper network $\mathcal{H}$ to parameterize a function $F$ which performs the mapping from inputs to outputs. We can then use $F$ to transform a new set of probe inputs (i.e. points we want to evaluate the polynomial at) to produce a set of predictions, and then train or evaluate the model on corresponding targets. \par 

@@

\textbf{The insight of our paper is that learning a meta-mapping over polynomials is exactly analogous to learning a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for the meta-mapping that operates over polynomials (e.g. multiplying by 2). Specifically, a set of polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding for each one. We then take a set of pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for the function that transforms one polynomial into another. Just as above, we pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are: 1) where the inputs and targets come from 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task. One of the main algorithmic insights of our work is that this produces $z^{func}$ embeddings which approximate the desired meta-mapping well, even for meta-mappings not included in training (see fig. 3). To evaluate meta-mapping performance, we actually computed the performance of the predicted output embedding at computing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was the function embedding of $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding input values to this function, and then measuring its predicted outputs against the real values of $2x+4$ at those inputs. We hope this clarifies our approach, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, and the algorithmic contribution is to show an approach for solving this challenge. Notably, because we use the same networks for both basic tasks and meta-mappings, our approach is parsimonious --- it does not require adding any new parameters to the model. (We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings.) While other meta-learning approaches could potentially be adapted to do meta-mappings, it is unclear that they could be adapted so parsimoniously, or perform well. However, we think exploring alternate approaches, or combining algorithms like MAML with architectures like ours, provide exciting future directions. For now, we are revising the main text to clarify our message. \par 

@@

\textbf{Architecture:} The reviewers noted that some of the architectural choices seemed arbitrary. We justify some choices in appendix D, but we acknowledge that we have not explored the full space of approaches to this problem, this will be important future work. On the DQN: the problem is not exactly a standard supervised problem because you have multiple betting actions and only observe the reward for the bet you execute, we have clarified this in the text. \par 

@@

\textbf{miniImageNet:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a 50-layer ResNet as the input encoder, we achieved test accuracy of 58.9\% on 5-shot, 5-way classification, competitive with e.g. MAML. We expect that given more than a few days to tune hyperparameters and architecture we could do much better. \par

@@

\textbf{Datasets:} Our tasks will be released on github as stand-alone python modules that other researchers can use. \par

@@

\textbf{Language \& continual learning:} We wanted to include language because it provides a simpler way to cue meta-mappings. Specifically, we used the language embedding as input to $H$ instead of using examples. For continual learning, while approaches like LEO generate (and even optimize) task embeddings, we are not aware of prior work that describes the continual learning approach of optimizing only the cached embeddings. Approaches like EWC double the parameter count by adding an ``importance'' parameter for each model parameter. For modern models with up to billions of parameters, caching a relatively low-dimensional task embedding instead would be advantageous even up to millions of tasks. In revising the paper, we will emphasize the main points before discussing these extensions. 
